---
title: "Week 4, Part 1 Condience intervals and t-tests lab"
author: "Elmera Azadpour"
date: "10/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Confidence intervals

```{r}
otter_length <- c(38,41,50,27,32,41,48,60,43)

t.test(otter_length)
```
## confidence interval means we would expect to find the pop mean within the range for the confidence interval presented


## 2. T-test (1-sample t-test)

See a claim: mean otter length is 50 inches 

```{r}
otter_test <- t.test(x=otter_length, mu=50)
otter_test
```
# alt hypothesis is meaningful now. Find that 0.0444 = p, if pop mean really is 50 in then there is 4.44% chance that I could have randomly taken a sample that has a mean that is a least as different from 50 as my sample mean is in either directions

## 3. Two sample t-test

```{r}
desert_bighorns <- c(32,44,18,26,50,33,42,20)
sierra_bighorns <- c(28,31,40,42,26,29,31)

t.test(x=desert_bighorns, y=sierra_bighorns)
```



